The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

This thesis is an attempt at finding out if different patterns in education lead to different outcomes in terms of start-up activities.

"Self-confidence in one's own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks" (OECD Report 2009).

>>>>

This thesis is an attempt at finding out if different patterns in education lead to different outcomes in terms of start-up activities. More specifically, we intend to look at self-esteem as partially the product of an education pattern, which would affect the whole population, even if so far, "self-confidence in one's own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks" (OECD Report 2009).
